Under-approximation of reachability in multivalued asynchronous networks

### 2013-04-02 parts/sa.tex
complete with substate reachability

%\newcommand{\total}{{total}}
%\newcommand{\reach}{{reach}}
\newcommand{\total}{\tau}
\newcommand{\reach}{\sigma}

We note that the semantics of PH with $2$ priorities defined in \pref{ssec:hypothesis} allows to model cooperative sorts representing a coherent configuration of a set of sorts.
As the method presented in this section allows to efficiently conclude on the reachability of a process,
we can derive a new method to conclude about the reachability of a state of components.
Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose we want to study the reachability of a state $s \in \PHl$.
Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$,
with: $\PHs' = \PHs \cup \{ \total, \reach \}$, $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
where $\total$ is a cooperative sort an all components $\components$ of $\PH$, thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$,
and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$.
We also define $\PHh'^{(1)}$ as the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHfrappe{\pfp_s(\total)}{\reach_0}{\reach_1} \}$;
therefore, the additional action in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of $s$ (considering only the components).

>>>>

\newcommand{\total}{\tau}
\newcommand{\reach}{\sigma}

We note that the semantics of PH with $2$ priorities defined in \pref{ssec:hypothesis} allows to model cooperative sorts representing a coherent configuration of a set of sorts.
As the method presented in this section allows to efficiently conclude on the reachability of a process,
we can derive a new method to conclude about the reachability of a state of components.
Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose we want to study the reachability of a state $s \in \PHl$.
Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$,
with: $\PHs' = \PHs \cup \{ \total, \reach \}$, $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
where $\total$ is a cooperative sort an all components $\components$ of $\PH$, thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$,
and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$.
We also define $\PHh'^{(1)}$ as the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHhit{\pfp_s(\total)}{\reach_0}{\reach_1} \}$.

Given an initial context $\ctx$, the reachability of $s$ in $\PH$ is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$ from the initial context $\ctx \cup \{ \reach_0 \}$ (the initial state of $\total$ does not matter), which can be under-approximated using \pref{th:approxinf}.
Indeed, the additional action $\PHhit{\pfp_s(\total)}{\reach_0}{\reach_1}$ in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of the state $s$ (considering only the components).
Moreover, it is possible to compute the reachability of a partial state by creating the sort $\total$ on a subset of $\components$,
or the reachability of a set of states $S \subset \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ for each state $s \in S$.
